### 2023-06-26 2023/certificates/gen_certificates_ornament.tex
[Results] Use the results with the fixed version of dolmen

\documentclass[landscape,12pt]{article}
\usepackage[svgnames]{xcolor}
\usepackage{wallpaper}
\usepackage{ragged2e}
\usepackage{ulem}
\usepackage[object=pgfhan]{pgfornament}
\usetikzlibrary{chains}
\usetikzlibrary{calc}
\usetikzlibrary{decorations}
\usetikzlibrary{decorations.text,decorations.markings}
\usetikzlibrary {decorations.pathmorphing,shadows}

@@

\fancyhead[L]{%
\newpgfornamentfamily{pgfhan}
\begin{tikzpicture}[overlay,remember picture]
    \tikzset{every node/.append style={inner sep=0pt,color=MidnightBlue!50}}
    \tikzset{pgfornamentstyle/.style={draw=green!20!black,
    fill=orange,fill opacity=.5,thick}}%
    \newbox{\fortyseven}
\savebox{\fortyseven}{\pgfornament[scale=0.50]{32}}
    \node[anchor=north west,shift={(14.5pt,-14.5pt)}] at (current page.north west)
  (nw) {\pgfornament[scale=0.5]{12}};
    \node[anchor=north east,shift={(-14.5pt,-14.5pt)}] at (current page.north east)
    (ne) {\pgfornament[scale=0.5,symmetry=v]{12}};
  \node[anchor=south west,shift={(14.5pt,14.5pt)}] at (current page.south west)
    (sw) {\pgfornament[scale=0.5,symmetry=h]{12}};
  \node[anchor=south east,shift={(-14.5pt,14.5pt)}] at (current page.south east)
    (se) {\pgfornament[scale=0.5,symmetry=c]{12}};
%    \pgfornamentline[scale=0.25,shift={(0pt,-14.5pt)}]{nw.north west}{ne}{20}{32};
% \begin{scope}[start chain,node distance=-1pt]
%     \node[anchor=north west,on chain] at (nw.north east)
%     {\usebox{\fortyseven}};
%     \foreach \i in {1,...,9} {\node[on chain]{\usebox{\fortyseven}};}
%     \end{scope}
\foreach \i in {0,...,5}
   \node[anchor=north west,shift={($\i*(100bp,0)$)}] at (nw.north east)
    {\usebox{\fortyseven}};
\foreach \i in {0,...,3}
    \node[anchor=south east,shift={($\i*(0,-100bp)$)},rotate=90] at (ne.south east)
     {\usebox{\fortyseven}};
\foreach \i in {0,...,5}
     \node[anchor=south west,shift={($\i*(100bp,0)$)}] at (sw.south east)
      {\usebox{\fortyseven}};
\foreach \i in {0,...,3}
      \node[anchor=south west,shift={($\i*(0,-100bp)$)},rotate=-90] at (nw.south west)
       {\usebox{\fortyseven}};
   %         \foreach \i in {0,...,22}
% \node[anchor=south west,rotate=-90,
% shift={($\i*(31bp,0)$)}] at (nw.south west)
% {\usebox{\fortyseven}};
    %   \node[anchor=north west] at (nw.north east) {\pgfornament[scale=0.25]{32}};
%    \draw [scale=0.25] (nw) to [ornament=12] (ne);
%   \node[anchor=north west] at (nw.north east)%
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south west] at (sw.south east)%
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south west,rotate=-90] at (nw.south west)
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south east,rotate=90] at (ne.south east)
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=center,shift={(25bp,-25bp)}] at (nw.south east)
%     {\pgfornament[scale=0.5]{57}};
\end{tikzpicture}
}

@@

 \medskip
\textcolor{red!30!black!90} {\textit{Certificate for category}}

>>>>

\documentclass[a4paper,landscape,12pt]{article}
\usepackage[svgnames]{xcolor}
\usepackage{wallpaper}
\usepackage{ragged2e}
\usepackage{ulem}
\usepackage[object=pgfhan]{pgfornament}
\usetikzlibrary{chains}
\usetikzlibrary{calc}
\usetikzlibrary{decorations}
\usetikzlibrary{decorations.text,decorations.markings}
\usetikzlibrary {decorations.pathmorphing,shadows}

@@

\fancyhead[L]{%
\newpgfornamentfamily{pgfhan}
\begin{tikzpicture}[overlay,remember picture]
    \tikzset{every node/.append style={inner sep=0pt,color=MidnightBlue!50}}
    \tikzset{pgfornamentstyle/.style={draw=green!20!black,
    fill=orange,fill opacity=.5,thick}}%
    \newbox{\fortyseven}
\savebox{\fortyseven}{\pgfornament[scale=0.50]{32}}
    \node[anchor=north west,shift={(14.5pt,-14.5pt)}] at (current page.north west)
  (nw) {\pgfornament[scale=0.5]{12}};
    \node[anchor=north east,shift={(-14.5pt,-14.5pt)}] at (current page.north east)
    (ne) {\pgfornament[scale=0.5,symmetry=v]{12}};
  \node[anchor=south west,shift={(14.5pt,14.5pt)}] at (current page.south west)
    (sw) {\pgfornament[scale=0.5,symmetry=h]{12}};
  \node[anchor=south east,shift={(-14.5pt,14.5pt)}] at (current page.south east)
    (se) {\pgfornament[scale=0.5,symmetry=c]{12}};
%    \pgfornamentline[scale=0.25,shift={(0pt,-14.5pt)}]{nw.north west}{ne}{20}{32};
% \begin{scope}[start chain,node distance=-1pt]
%     \node[anchor=north west,on chain] at (nw.north east)
%     {\usebox{\fortyseven}};
%     \foreach \i in {1,...,9} {\node[on chain]{\usebox{\fortyseven}};}
%     \end{scope}
\foreach \i in {0,...,6}
   \node[anchor=north west,shift={($\i*(100bp,0)-(50bp,0)$)}] at (nw.north east)
    {\usebox{\fortyseven}};
\foreach \i in {0,...,3}
    \node[anchor=south east,shift={($\i*(0,-100bp)$)},rotate=90] at (ne.south east)
     {\usebox{\fortyseven}};
\foreach \i in {0,...,6}
     \node[anchor=south west,shift={($\i*(100bp,0)-(50bp,0)$)}] at (sw.south east)
      {\usebox{\fortyseven}};
\foreach \i in {0,...,3}
      \node[anchor=south west,shift={($\i*(0,-100bp)$)},rotate=-90] at (nw.south west)
       {\usebox{\fortyseven}};
   %         \foreach \i in {0,...,22}
% \node[anchor=south west,rotate=-90,
% shift={($\i*(31bp,0)$)}] at (nw.south west)
% {\usebox{\fortyseven}};
    %   \node[anchor=north west] at (nw.north east) {\pgfornament[scale=0.25]{32}};
%    \draw [scale=0.25] (nw) to [ornament=12] (ne);
%   \node[anchor=north west] at (nw.north east)%
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south west] at (sw.south east)%
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south west,rotate=-90] at (nw.south west)
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=south east,rotate=90] at (ne.south east)
%     {\pgfornament[scale=0.25]{32}};
%     \node[anchor=center,shift={(25bp,-25bp)}] at (nw.south east)
%     {\pgfornament[scale=0.5]{57}};
\end{tikzpicture}
}

@@

 \medskip
\textcolor{red!30!black!90} {\textit{Certificate for divisions}}
